Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-16 tex/MesnardoBarba2019.tex
Add Zenodo archive citation

In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
The repository is found at \url{https://github.com/barbagroup/cloud-repro}.
Our expanded reproducibility packages contain input files, Batch Shipyard configuration files, command-line instructions to set up and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available. 
These files contain details about all the libraries needed to create the computational runtime environment.
We even include a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again.

>>>>

In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
The repository is found at \url{https://github.com/barbagroup/cloud-repro}.
Our expanded reproducibility packages contain input files, Batch Shipyard configuration files, command-line instructions to set up and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available. 
These files contain details about all the libraries needed to create the computational runtime environment.
We even include a Dockerfile to reproduce the local environment with the visualization tools needed for post-processing.
In addition, we have also deposited in the Zenodo service all secondary data required to reproduce the figures of the paper without running the simulations again\cite{cloud_repro_2019}.
